Katana: Towards Patching as a Part of the ELF Toolchain

### 2010-03-18 paper1/hotpatch/intro.tex
changed the title and moved around the conficker quote

It is somewhat ironic that users and organizatations hesistate to
apply patches whose stated purpose is to support availability or
reliability precisely because the process of doing so can lead to
downtime (both from the patching process itself as well as
unanticipated issues with the patch).  Periodic reboots in desktop
systems --- irrespective of the vendor --- are at best annoying.
Reboots in enterprise environments ({\it e.g.,} trading, e-commerce,
core network systems), even for a few minutes, imply large revenue
loss or an extensive backup and failover infrastructure with rolling
updates.  We question whether this {\em de facto} acceptence of
significant downtime and redundant infrastructure should not be
abandoned in favor of a reliable hot patching process.

>>>>

It is somewhat ironic that users and organizatations hesistate to
apply patches whose stated purpose is to support availability or
reliability precisely because the process of doing so can lead to
downtime (both from the patching process itself as well as
unanticipated issues with the patch).  Periodic reboots in desktop
systems --- irrespective of the vendor --- are at best annoying.
Reboots in enterprise environments ({\it e.g.,} trading, e-commerce,
core network systems), even for a few minutes, imply large revenue
loss or an extensive backup and failover infrastructure with rolling
updates.  
{\footnotesize
\begin{quote}
``Some reports, such as the case of the Conficker outbreak within 
Sheffield Hospital's operating ward, suggest that even security-
conscious environments may elect to forgo automated software patching, 
choosing to trade off vulnerability exposure for some perceived notion 
of platform stability...'' -- \url{http://mtc.sri.com/Conficker/}
\end{quote}
}
We question whether this {\em de facto} acceptence of
significant downtime and redundant infrastructure should not be
abandoned in favor of a reliable hot patching process.

### 2010-03-18 paper1/hotpatch/secse-main.tex
use APA bibliographic style
back to using abbrv bib style until I figure out how it's actually supposed to be
changed the title and moved around the conficker quote

\documentclass[10pt, conference, compsocconf]{IEEEtran}
\IEEEoverridecommandlockouts % for \thanks
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{url}
%\usepackage{hyperref} -- DISABLED: fails ``PDF express'' check

@@

\title{Katana: A Hot Patching Framework for ELF Executables}

@@

{\footnotesize
\begin{quote}
``Some reports, such as the case of the Conficker outbreak within 
Sheffield Hospital's operating ward, suggest that even security-
conscious environments may elect to forgo automated software patching, 
choosing to trade off vulnerability exposure for some perceived notion 
of platform stability...'' -- \url{http://mtc.sri.com/Conficker/}
\end{quote}
}

@@

{\small
\bibliographystyle{abbrv}
\bibliography{locasto,extras,oakley}
}

>>>>

\documentclass[10pt, conference, compsocconf]{IEEEtran}
\IEEEoverridecommandlockouts % for \thanks
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{hyperref} -- DISABLED: fails ``PDF express'' check

@@

\title{Katana: Towards Patching as a Part of the ELF Toolchain}

@@

@@

{\small
%\bibliographystyle{apa-good}
\bibliographystyle{abbrv}
\bibliography{locasto,extras,oakley}
}
